\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-05 ms.tex
fig
Update on Overleaf.

We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on a portion of the cluster discovered using the \gaia\ data (see previous section).
\todo{Nidever: can you describe the observations? Exposure times, dither, whatever is usually done...}

The photometry was reduced...\todo{Nidever: describe your pipeline?}

@@

% Notebook: Figure-hierarch-results
\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{figures/hierarch-results.pdf}
\caption{The \decam\ color-magnitude diagram for sources with probabilty $>0.5$ of belonging to \clustername\ (markers).
The solid line (blue) shows the \acronym{MIST} isochrone for the median posterior sample from the hierarchical inference of the cluster population parameters, shifted to the inferred distance to \clustername, and extincted with the inferred extinction.
The dashed line (green) shows the same isochrone, shifted $\approx 0.75$ magnitudes brighter, representing the expected location of the equal-mass binary sequence of the cluster.
}
\label{fig:hierarch-iso}
\end{figure}

@@

% TODO: Nidever plots at different velocities?
Here we take a closer look at the \hi gas in the vicinity of \clustername.
\figurename~\ref{fig:XXXX} shows the \hi column density in the region around the leading arm of the Magellanic stream, with the location of \clustername\ marked.
While no bulk metallicity measurements exist for the LA gas, \todo{...recent measurements suggest comparable to SMC?} \citep{Fox:2018}.
Given its extragalactic origin, its proximity to the Magellanic stream suggests that \clustername\ could have formed from this gas.
Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, MoniBidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.

@@

\begin{figure}
\centering
\includegraphics[width=8cm]{gass_vlsrmlon.pdf}
\caption{GASS position-velocity diagram.}
\label{fig_gass}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=8cm]{gass_mlatmlon.pdf}
\caption{GASS \hi column density in the region of LA II. The red cross marks the position
of the young cluster.}
\label{fig_gass}
\end{figure}

@@

>>>>

We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on a portion of the cluster discovered using the \gaia\ data (see previous section).  Observations were obtained with the Dark Energy Camera (DECam) on the CTIO 4m Blanco telescope on UT 2018 May 20 with 3$\times$300s
exposures in $u-$, $g-$, and $i$-band.  The NOAO Community Pipeline (CP; \citealt{Valdes:2014}; Valdes et al., in preparation) InstCal images, which have the instrumental signature removed, were downloaded from the NOAO Archive\footnote{\url{http://archive.noao.edu}} for further processing.  Forced PSF photometry was performed with the PHOTRED pipeline \citep{Nidever:2017} which uses the DAOPHOT ALLSTAR \citep{Stetson:1987} and ALLFRAME \citep{Stetson:1994} suite of programs.  The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for
global zero-point and color-terms in each band.
%\todo{Nidever: can you describe the observations? Exposure times, dither, whatever is usually done...}
%The photometry was reduced...\todo{Nidever: describe your pipeline?}

@@

% Notebook: Figure-hierarch-results
\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/hierarch-results.pdf}
\caption{The \decam\ color-magnitude diagram for sources with probabilty $>0.5$ of belonging to \clustername\ (markers).
The solid line (blue) shows the \acronym{MIST} isochrone for the median posterior sample from the hierarchical inference of the cluster population parameters, shifted to the inferred distance to \clustername, and extincted with the inferred extinction.
The dashed line (green) shows the same isochrone, shifted $\approx 0.75$ magnitudes brighter, representing the expected location of the equal-mass binary sequence of the cluster.
}
\label{fig:hierarch-iso}
\end{figure}

@@

% TODO: Nidever plots at different velocities?
Here we take a closer look at the \hi gas in the vicinity of \clustername.
\figurename~\ref{fig:gass_maps} shows the \hi column density of the catalog of Gaussian centers \citep[producted with the techniques and software from][]{Nidever:2008} from the Galactic All Sky Survey \citep[GASS;][]{McClure-Griffiths:2009,Kalberla:2010} in the region around the Leading Arm of the Magellanic stream, with the location of \clustername\ marked.
While no bulk metallicity measurements exist for the LA gas, \todo{...recent measurements suggest comparable to SMC?} \citep{Fox:2018}.
Given its extragalactic origin, its proximity to the Magellanic stream suggests that \clustername\ could have formed from this gas.
Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, Moni-Bidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.

@@

\begin{figure}
\centering
\includegraphics[width=8cm]{figures/gass_vlsrmlon.pdf}
\caption{The position-velocity diagram of GASS Gaussian centers.}
\label{fig:gasspv}
\end{figure}

\begin{figure}
\centering
%\includegraphics[width=8cm]{gass_mlatmlon.pdf}
\includegraphics[width=8cm]{figures/gass_maps_v2.pdf}
\caption{GASS \hi column density in the region of LA II at three different velocities.
The red circle marks the position of the young cluster.}
\label{fig:gass_maps}
\end{figure}

@@

D.L.N thanks Peter Kalberla for making the GASS datacubes available in Magellanic Stream coordinates.
